SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-02-03 sedona-ieice16/revision/paper.tex
SEDONA paper updates

Measuring program execution time is a much-used
technique for performance evaluation in computer science. 
Despite the importance of accurate and precise execution-time measurement, 
how to achieve {\em better} timing has not been well addressed. 
{\color{blue} Surprisingly, there is considerable variability in the measured time.
%which indeed suggests the need for a better timing protocol.
The goal of this paper is to propose
a better timing protocol that can significantly reduce such variability 
and thus enable better timing results without a doubt of their validity.}

@@

{\color{blue}
Our protocol, which we propose shortly, on the contrary, 
effectively identifies and removes those outliers. 
In effect, the protocol considerably reduces such variability.
The protocol identified and removed fifteen repetitions 
that had {\em infrequent, \hbox{long-running} daemon processes}, 
impacting the execution time of PUT128. 
In addition, the protocol utilized {\em process time} (PT) (of PUT128) 
rather than elapsed time (ET). 
Using PT is preferred, in that it considers 
the time taken for only a process of interest.
PT can be calculated as the sum of ticks (where one tick is equal to 10 msec)
in user and system mode, available via {\tt taskstats} C struct, 
provided by the Linux NetLink facility~\cite{Netlink}.
As a result, none of the retained timing results was outside of 
the central band in Fig.~\ref{fig:hist_after_pt}, and thus 
the measurement quality---in both standard deviation and relative error---was 
improved up to by three orders of magnitude for PUT128, 
as shown in Fig.~\ref{fig:hist_after_pt}.
}

>>>>

Measuring program execution time is a much-used
technique for performance evaluation in computer science. 
Despite the importance of accurate and precise execution-time measurement, 
how to achieve {\em better} timing has not been well addressed. 
Surprisingly, there is considerable variability in the measured time.
%which indeed suggests the need for a better timing protocol.
{\color{red} The goal of this paper is to propose
a better timing protocol that can significantly reduce such variability 
and thus enable better timing results without a doubt of their validity.}

@@

{\color{blue}
Our protocol, which we characterize shortly, on the contrary, 
exactly identified and removed those outliers. 
In effect, the protocol considerably reduced such variability, 
as illustrated in Fig.~\ref{fig:hist_after_pt}. 
Specifically, regarding standard deviation and relative error 
the protocol presented a significant performance gain up to by 
three orders of magnitude for the same PUT128 results.
}

{\color{red}
{\bf Characteristics.} There are several distinctions of our protocol. 
First, we utilize {\em process time} (PT) rather than on elapsed time (ET). 
The use of PT is preferred, as it takes into account 
the time taken for only a ``process'' (or program) of interest.
PT is defined as the sum of ticks (where one tick is equal to 10 msec)
in user and system mode. 
These tick measures are obtainable via {\tt taskstats} C struct, 
provided by the Linux NetLink facility~\cite{Netlink}. 
Second, the protocol throws out some repetitions that involve
{\em infrequent, \hbox{long-running} daemon processes}. 
We observe that such daemon processes substantially impact 
the execution time of the process.  
By eliminating those repetitions, the protocol greatly improves
the overall measurement quality, which would otherwise be biased by them.
}
%The protocol thus can considerably reduce such variability.
%The protocol identified and removed fifteen repetitions 
%that had {\em infrequent, \hbox{long-running} daemon processes}, 
%impacting the execution time of PUT128. 
%As a result, none of the retained timing results was outside of 
%the central band in Fig.~\ref{fig:hist_after_pt}, and thus 
%the measurement quality---in both standard deviation and relative error---was 
%improved up to by three orders of magnitude for PUT128, 
%as shown in Fig.~\ref{fig:hist_after_pt}.

%In addition, the protocol utilized {\em process time} (PT) (of PUT128) 
%rather than elapsed time (ET). 
%Using PT is preferred, in that it considers 
%the time taken for only a process of interest.
%PT can be calculated as the sum of ticks (where one tick is equal to 10 msec)
%in user and system mode, available via {\tt taskstats} C struct, 
%provided by the Linux NetLink facility~\cite{Netlink}.
